Turbulence in compact to giant HII regions

### 2022-03-04 strucfunc_paper.tex
Javier changes 2022-03-04

We present the second-order structure results plotted against separation in parsecs and the posteriors of the turbulent parameters.

@@

Figure~\ref{fig:strucfunc-fit-OrionS}a shows that the structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
Small scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{2}{\arcsecond}), which only affects the first point.
From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they affected at some extent by the seeing. 
The correlation length for the Orion core is 0.07\(\pm\)0.01 pc with a \(\sigma^2\pos\) of 13\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
At large scales there is a small plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
Above separations of \SI{0.3}{pc} the structure function decays a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.

In the Figure~\ref{fig:strucfunc-fit-M8}a we see that the Lagoon nebula presents some particular behavior at small and large scales. 
At small scales, considered above the separation of \SI{0.005}{pc} (\(s_0\)=\SI{0.83}{\arcsecond}), the structure function shows the characteristic ascending values despite not being as uniform as the other regions.
In this case there aren't points affected by the seeing.
However, there is a clear tendency of a power-law behavior that fits our model with a \(r_0\) of 1\(\pm\)0.2 pc and a \(\sigma^2\pos\) of 7\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
The first maximum value of \(B(r)\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then at \(\sim\)\SI{4.5}{pc} the minimum value, \(\sim\)\SI{11}{km^{2}.s^{-2}}, of the first oscillation is reached.
From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} at \SI{20}{pc}.

At small scales the Carina structure function, Figure~\ref{fig:strucfunc-fit-CarC}a, shows the most erratic behavior of all our sample.
Despite this lack of uniformity, still it is possible to see a series of ascending values indicating the existence of correlations in the velocity field that fits our proposed model.
The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there aren't any points that lie below the true model as in the Lagoon nebula.
The correlation length is 0.56\(\pm\)0.04 pc at a \(\sigma^2\pos\) of 18\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.

For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
Instead the discrete fiber positions are diversely located across the FOV.
This would affect the structure function since the values are not adjacent as the other observations.
This is reflected in the non uniform \(B(r)\) values at small scales that we point in the previous paragraphs.

In the Figure~\ref{fig:strucfunc-fit-N346}a we show the structure function of NGC 346.
For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) but still the first 8 points lie below the true model.
At separations above \SI{0.4}{pc} the structure functions observed values coincide with the true model. 
The correlation length is 2\(\pm\)0.1 pc at a \(\sigma^2\pos\) of 37\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
For larger scales a periodic behavior is seen above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}}.
Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
The correlation length is 4\(\pm\)0.2 pc at a \(\sigma^2\pos\) of 300\(\pm\)9 \(\text{km}^2 \text{s}^{-2}\).
As the Orion core, 30 Doradus structure function presents a behavior of tapered fluctuations.  
The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
The structure function is well behaved with our model and present characteristics of tapered fluctuations with a small periodic behavior.
The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond})..
Despite this seeing value, all the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
The correlation length is 3.4\(\pm\)0.3 pc with a \(\sigma^2\pos\) of 10\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, there is a rise in \(B(r)\) for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
The correlation length is 4\(\pm\)0.4 pc at a \(\sigma^2\pos\) of 16\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
The structure functions presents at large scales the behavior of periodic fluctuations.
A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise in \(B(r)\) to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first point is below the true model and starting from \SI{2}{pc} there is a good agreement between the observed structure function.
The correlation length is 12\(\pm\)1 pc at a \(\sigma^2\pos\) of 56\(\pm\)2 \(\text{km}^2 \text{s}^{-2}\).
At large scales the structure function behave following the tapered fluctuations behavior.
A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
The structure function present clear characteristics of periodic oscillations at large scales.
The seeing is \SI{2.2}{pc} (\(s_0\)=\SI{0.53}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
The correlation length is 9\(\pm\)3 pc at a \(\sigma^2\pos\) of 81\(\pm\)25 \(\text{km}^2 \text{s}^{-2}\).
A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.

>>>>

In this section we present and describe the second-order structure results. The structure functions are plotted against separation in parsecs and we also show the posteriors of the turbulent parameters using the analysis discussed in section~\ref{sec:methods-apply}.

@@

Figure~\ref{fig:strucfunc-fit-OrionS}a shows that the structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
Small scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{2}{\arcsecond}), which only affects the first point.
From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they affected at some extent by the seeing. 
The correlation length for the Orion core is 0.07\(\pm\)0.01 pc, it has a \(\sigma^2\pos\) of 13\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.07\(\pm\)0.02.
At large scales there is a plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
Above separations of \SI{0.3}{pc} the structure function decays reaching a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.

In the Figure~\ref{fig:strucfunc-fit-M8}a we see that the Lagoon nebula presents a non-uni from behavior at small. 
In this range considered above the separation of \SI{0.005}{pc} (\(s_0\)=\SI{0.83}{\arcsecond}) there aren't points affected by the seeing.
The structure function shows the characteristic ascending values despite not being as uniform as the other regions.
The turbulent parameters that fits our model are a \(r_0\) of 1\(\pm\)0.2 pc, a \(\sigma^2\pos\) of 7\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.13\(\pm\)0.01.
At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
The first maximum value of \(B(r)\) in the order of 2\(\sigma^2\pos\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Considering an oscillating behavior at \SI{4.5}{pc} a minimum value of \SI{11}{km^{2}.s^{-2}} is reached.
From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} around \SI{20}{pc}.

At small scales the Carina structure function, Figure~\ref{fig:strucfunc-fit-CarC}a, shows the most erratic behavior of all our sample.
Despite this lack of uniformity, still it is possible to see a series of ascending values indicating the existence of correlations in the velocity field that fits our proposed model.
The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there aren't many points that lie below.
The correlation length is 0.56\(\pm\)0.04 pc at a \(\sigma^2\pos\) of 18\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.14\(\pm\)0.01.
At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.

For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
Instead the discrete fiber positions are diversely located across the FOV.
This would affect the structure function since the values are not adjacent as the other observations.
This is reflected in the non uniform \(B(r)\) below  \(r_0\) that we pointed out in the previous paragraphs.

In the Figure~\ref{fig:strucfunc-fit-N346}a we show the structure function of NGC 346.
For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) but the first 8 points lie below the true model.
At separations above \SI{0.4}{pc} the structure functions observed values coincide with the true model. 
The correlation length is 2\(\pm\)0.1 pc at a \(\sigma^2\pos\) of 37\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.76\(\pm\)0.02.
For scales above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}} a periodic behavior is seen .
Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
The correlation length is 4\(\pm\)0.2 pc at a \(\sigma^2\pos\) of 300\(\pm\)9 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.84\(\pm\)0.04.
As the Orion core, 30 Doradus structure function presents a behavior of tapered fluctuations.  
The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}).
Despite this seeing value, all the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
The correlation length is 3.4\(\pm\)0.3 pc at a \(\sigma^2\pos\) of 10\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.74\(\pm\)0.10.
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, then it rises for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
The correlation length is 4\(\pm\)0.4 pc at a \(\sigma^2\pos\) of 16\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\) and an index of 0.88\(\pm\)0.14.
The structure functions presents at large scales the behavior of periodic fluctuations.
A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise in \(B(r)\) up to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first point is below the true model and starting from \SI{2}{pc} there is a good agreement between the observed structure function.
The correlation length is 12\(\pm\)1 pc at a \(\sigma^2\pos\) of 56\(\pm\)2 \(\text{km}^2 \text{s}^{-2}\) and an index of 1.3\(\pm\)0.05.
At large scales the structure function behave following the tapered fluctuations behavior.
A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N604H}a we show the structure function of NGC 604.
The structure function present clear characteristics of periodic oscillations at large scales.
The seeing is \SI{2.2}{pc} (\(s_0\)=\SI{0.53}{\arcsecond}) and the structure function of this region lies below the true model for most of the separation range.
The correlation length is 9\(\pm\)3 pc at a \(\sigma^2\pos\) of 81\(\pm\)25 \(\text{km}^2 \text{s}^{-2}\) and has an index of 1.3\(\pm\)0.05.
A periodic pattern for the structure function appears with a maximum \(B(r)\) value of \SI{143}{km^{2}.s^{-2}} that is reached at \SI{60}{pc}, then the oscillation cause a minimum of \SI{54}{km^{2}.s^{-2}} at \SI{133}{pc} and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
